Effects of epidemiological structure on the transient evolution of HIV virulence

### 2017-02-03 ms/ms.tex
add to discussion

>>>>

How contact structures are modeled can strongly affect
researchers' conclusions about the evolutionary dynamics of
virulence. In particular, a relatively simple (strategic) 
eco-evolutionary model of HIV can predict peak $\log_{10}$
set-point viral loads (over the course of an epidemic)
ranging from 3.5 to 4.8 depending on the specific model
of sexual partnership behaviour used. This difference in \Lspvl\ is
epidemiologically significant, corresponding to a twofold difference
(12 vs. 6 years) in expected time to progression.

Surprisingly, the biggest differences are not between the simplest
and the most complex contact structures, but between the
complex contact structures and models of \emph{intermediate}
complexity. These intermediate-complexity models attempt,
quite reasonably, to add at least some of the realism of
human sexual behaviour, but leave out apparently insignificant
details such as extra-pair contact. If partial complexity
may lead to such mistakes, how can modelers do anything but always
strive to build the most realistic models possible?
